Top-down Segment-based Neuron Reconstruction

### 2017-11-10 papers/cvpr2018/0_introduction.tex
paper: updated entire paper

Segmenting the image stack into a label volume is a substantial component of this reconstruction process.
In a label volume, every voxel receives a segment label corresponding to a unique neuron. 
Voxels with the same label belong to the same neuron.
It is not feasible for domain experts to manually segment the vast amount of 3-D image data to model an entire brain.
Here we introduce a scalable top-down segmentation algorithm that also leverages local information.
The top-down partitioning strategy allows us to apply domain-specific constraints to the segmentation task.

@@

Researchers currently address the failures of these pixel-based algorithms by training random-forest classifiers to agglomerate an oversegmentation of voxels~\cite{nunez2014graph,10.1371/journal.pone.0125825}.
These classifiers take the output of the pixel-based algorithms as input and generate high-level statistics such as affinity distributions between pixel regions. 
Presently, these methods use hand-designed features despite the evidence that machine-learned features perform better~\cite{bogovic2013learned}. 
These \textit{region-based} algorithms outperform the pixel-based algorithms but still do not provide the accuracy needed for large scale reconstructions of the brain.

We present a \textit{segment-based} strategy that extends on the outputs of region-based methods.
We only take as input a segmentation from a previous agglomeration algorithm and not the raw image data. 
This allows us to train on connectomics datasets at a resolution and image type different than the test datasets.
We consider the 3-D skeletons of each segments as a simplification of its shape. 
We can then quickly extract a graph from the input segmentation using the skeletonization of the segments in the volume.

We add edge weights to our graph using a 3-D CNN to predict the probabilities that nearby segments belong to the same neuron.
Using a graph-based optimization strategy enables us to enforce domain-specific global constraints such as the underlying neuronal biology.
From here we apply a global partitioning algorithm that minimizes a cost function of separating adjacent nodes in the graph.

Our method takes the output of any bottom-up segmentation strategy and creates a graph on top of this segmentation. 
We enforce domain-specific global constraints by reasoning at the graph level.
This strategy scales to massive connectomics datasets and improves accuracy over existing methods.

>>>>

Segmenting the image stack into a label volume is a substantial component of this reconstruction process.
In a label volume, every voxel receives a segment label corresponding to a unique neuron. 
Voxels with the same label belong to the same neuron.
It is not feasible for domain experts to manually segment the vast amount of 3-D image data to model an entire brain.
Here we introduce a scalable, top-down segmentation algorithm that also leverages local information.
Partitioning from a top-down approach allows us to apply domain-specific constraints to the segmentation task.

@@

Researchers address the failures of these pixel-based algorithms by training random-forest classifiers to agglomerate an oversegmentation of voxels~\cite{nunez2014graph,10.1371/journal.pone.0125825}.
These classifiers take the output of the pixel-based algorithms as input and generate high-level statistics such as affinity distributions between regions. 
Presently, these methods use hand-designed features despite the evidence that machine-learned features perform better~\cite{bogovic2013learned}. 
These \textit{region-based} algorithms outperform the pixel-based algorithms but do not provide the accuracy needed for large scale reconstructions of the brain.

We present a \textit{segment-based} strategy that builds on the outputs of region-based methods (Figure \ref{fig:teaser}).
We only take as input a segmentation from the region-based agglomeration algorithm. 
This allows us to train on connectomics datasets at a given resolution and image type and test on another resolution.
This is a huge plus considering the sheer amount of expert-hours needed to generate ground truth for these massive datasets.
We extract a graph representation from the input segmentation.
By simplifying the 3-D segments by their skeletons, we can quickly generate the graph nodes and edges. 
We train a 3-D CNN to populate the graph edge weights with bottom-up local information. 
We enforce domain-specific global constraints, such as the underlying biology, using a graph-based partitioning heuristic.
In this we can leverage both local and global information to produce a more accurate segmentation.

Our novel approach creates a level of abstraction over existing region-based agglomeration strategies. 
We take the output of these methods as input and extract a graph structure from that.
This allows us to enforce restrictions on our output that closely follow the underlying biology of these connectomics datasets. 
We use bottom-up information to weight the edges in our graph and top-down information when partitioning the graph. 
This dual approach of assessing local decisions in a global framework produces improvements over the existing region-based methods.

### 2017-11-10 papers/cvpr2018/1_related_work.tex
paper: updated entire paper

A significant amount of research in computer vision focuses segmentation of images \cite{zaitoun2015survey}. 
Here, we review some of the most successful methods that have been applied to large-scale EM images.

@@

A large amount of connectomics research considers the problem of extracting segmentation information at the voxel level from the raw EM images to produce label volumes.
Some early techniques apply computationally expensive graph partitioning techniques with a single node per voxel  \cite{andres2012globally}, however these methods do not scale to terabyte datasets.
Since then, several methods train 2-D CNNs to predict membrane probabilities per image slice~\cite{ciresan2012deep,jain2010boundary,kaynig2015large,rhoananet,amelio_segmentation}. 
More recent strategies augment these neural networks with the $z$-dimension creating full 3-D CNNs~\cite{lee2015recursive,ronneberger2015u}.
Oftentimes these networks produce probabilities for the affinity between voxels, i.e., the probability that adjacent voxels belong to the same neuron.
More recently, flood-filling networks produce segmentations by training an end-to-end neural network that takes EM images to label volumes~\cite{januszewski2016flood}.
These networks produce very impressive accuracies but are much too slow to scale to larger datasets.

@@

Several of these pixel-based approaches generate probabilities that neighboring voxels belong to the same neuron.
Many algorithms build on top of these methods and train random-forest classifiers to produce segmentations of the EM images~\cite{seymour2016rhoananet,nunez2014graph,10.1371/journal.pone.0125825,parag2017anisotropic,zlateski2015image}. 
Despite the success of these classifiers, they often make mistakes based on the local information leading to errors in the segmentation. 
Additionally, many recent advancements in segmentation use artificial neural networks given the evidence that machine-learned features outperform hand-designed ones~\cite{bogovic2013learned}.
A significant amount of research focuses on the training and optimization of these deep neural networks~\cite{chatfield2014return,maas2013rectifier,nesterov1983method}.

@@

Some limited research builds on top of the region-based methods to correct errors in the segmentation \cite{rolnick2017morphological,error_correction_using_CNN}.
Similarly, proofreading methods create a ``human-in-the-loop" framework that allows users to find errors and correct them \cite{haehn2017scalable,haehn2017guided,haehn2014design}. 
Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}. 
The multicut graph partitioning algorithm produces a set of segments where no segment contains a cycles.
This closely resembles the biological constraint that neurons have a topological genus of zero. 
Unfortunately the graph partitioning formulation is NP-Hard~\cite{demaine2006correlation}.
However, there are several useful multicut heuristics which provide good approximations with reasonable computational costs~\cite{horvnakova2017analysis,kernighan1970efficient,keuper2015efficient}.

>>>>

A significant amount of research in computer vision focuses on the segmentation of images \cite{zaitoun2015survey}. 
Here, we review some of the most successful methods that have been applied to large-scale EM images. Figure \ref{fig:pipeline} shows the results of a typical segmentation pipeline on these images.

@@

A large amount of connectomics research considers the problem of extracting segmentation information at the voxel level from the raw EM images to produce label volumes.
Some early techniques apply computationally expensive graph partitioning algorithms with a single node per voxel~\cite{andres2012globally}, however these methods do not scale to terabyte datasets.
Since then, several methods train 2-D CNNs to predict membrane probabilities per image slice~\cite{ciresan2012deep,jain2010boundary,kaynig2015large,rhoananet,amelio_segmentation}. 
More recent strategies augment these neural networks with the $z$-dimension creating full 3-D CNNs~\cite{lee2015recursive,ronneberger2015u}.
Oftentimes these networks produce probabilities for the affinity between two voxels (i.e., the probability that adjacent voxels belong to the same neuron).
The MALIS cost function is specifically designed for generating affinities that produce good segmentations~\cite{briggman2009maximin}. 
More recently, flood-filling networks produce segmentations by training an end-to-end neural network that takes EM images to label volumes~\cite{januszewski2016flood}.
These flood-filling networks produce very impressive accuracies but at too high a computational cost.

@@

Several of these pixel-based approaches generate probabilities that neighboring voxels belong to the same neuron.
Many algorithms build on top of these methods and train random-forest classifiers to produce segmentations of the EM images~\cite{seymour2016rhoananet,nunez2014graph,10.1371/journal.pone.0125825,parag2017anisotropic,zlateski2015image}. 
Despite the success of these classifiers, they often make mistakes based on the local information leading to errors in the segmentation. 
Lately, many recent advancements in segmentation use artificial neural networks since machine-learned features outperform hand-designed ones~\cite{bogovic2013learned}.
A significant amount of research focuses on the training and optimization of these deep neural networks~\cite{chatfield2014return,maas2013rectifier,nesterov1983method}.

@@

Some limited research builds on top of the region-based methods to correct errors in the segmentation \cite{rolnick2017morphological,error_correction_using_CNN,haehn2017guided}. 
However, to our knowledge, we are the first to extract a graph representation from these region-based methods. 
Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for traditional image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}. 
We can enforce domain-specific constraints using graph-based paritioning algorithms.  
Unfortunately graph partitioning is an NP-Hard problem~\cite{demaine2006correlation}.
However, there are several useful multicut heuristics which provide good approximations with reasonable computational costs~\cite{horvnakova2017analysis,keuper2015efficient}.

### 2017-11-10 papers/cvpr2018/2_method.tex
paper: updated entire paper

\subsection{Graph Creation}

We generate nodes $N$ and edges $E$ to apply a graph-based optimization strategy for segmentation. 
In addition, these edges need non-negative weights.

@@

The simplest node generation strategy creates one node for every unique segment label in the input volume.
However, some of the millions of labels in the volume correspond to very small regions. 
Usually these locations have noisy image data so the voxel-based methods could not provide enough information to generate a larger segment.
It is difficult to extract useful shape features from these segments because of their small, and often random, shape. 
We prune these nodes from the graph by removing all segments with fewer than $20,000$ voxels. 
On a typical connectomics dataset this only remove XX$\%$ of segments.

@@

A na\"ive approach to generating edges produces an edge between all adjacent segments.
Two segments $l_1$ and $l_2$ are considered adjacent if there is a pair of adjacent voxels where one has label $l_1$ and the other has label $l_2$. 
NeuroProof and GALA consider all pairs of adjacent segments for merging. 
This method produces too many edges in the graph for us.
Therefore we present the following algorithm to identify pairs of segments to consider merging.

First, we extract a skeleton from each segment using the TEASER algorithm~\cite{sato2000teasar,zhao2014automatic}.
Figure~\ref{fig:skeletonization} shows the skeletons in white of two segments from the label volume.
These skeletons consist of a sequence of \textit{joints}, locations that are a local maximum distance from the segment boundary, with line segments connecting successive joints. 
We prune the joints that are within $50$ voxels of each other to reduce unnecessary branching.
For the purposes of our algorithm, joints that have only one connected neighbor are referred to as \textit{endpoints}. 
Many of the segments that are erroneously split follow a similar pattern (Figure~\ref{fig:merge_candidates}). 
In these split instances the skeletons have nearby endpoints.

After skeletonization, we begin to identify segments for merge consideration with the following two-pass heuristic.
In the first pass, we iterate over all endpoints $e$ belonging to a segment $S$ and create a set of segments $\mathbb{S}_e^\prime$ that includes all labels that have a single voxel within $t_{low}$ voxels from $e$. 
Elements of these sets are candidates for merging.
However the first pass often has too many candidates that should remain split so we apply an additional pass for further pruning.
In the second pass, we consider all of the segments $\mathbb{S}_e^\prime$ for every endpoint $e$. 
If a segment $S^\prime \in \mathbb{S}_e^\prime$ has an endpoint within $t_{high}$ voxels of $e$, the segment $S$ and $S^\prime$ are considered for merging. 
We store the midpoint between the two endpoints as the ``center" of the potential merge.
Algorithm (ADD REF) provides pseudocode for this edge generation algorithm.

\begin{figure}[t]
	\centering
	\includegraphics[width=0.92\linewidth]{./figures/split_error1.png}
	\includegraphics[width=0.92\linewidth]{./figures/split_error2.png}
	\caption{Two erroneously split segments that should merge together. Most segments that we want to merge have the same general structure.}
	\label{fig:merge_candidates}
\end{figure}

\begin{algorithmic}
	\Function{GenerateEdges}{$skeletons$}
		\For {$skeleton$ in $skeletons$}
			\State $candidates$ = set()
			\For {$endpoint$ in $skeleton$}
				\State TODO ADD CODE
			\EndFor
		\EndFor
	\EndFunction
\end{algorithmic}

Note that this algorithm does not enforce any segment adjacency constraints.
Figure (ADD FIGURE) shows two examples that would not be considered in NeuroProof or GALA since these algorithms only consider merging adjacent segments.

@@

Our graph generation algorithm produces 3-D locations that require further consideration for merging. 
To determine which of these segments should actually merge, we train a 3-D CNN using the oversegmentation and the corresponding manually labeled ground truth data (Section~\ref{sec:dataset}).
We extract a cubic region of interest around these locations as input to the CNN. 
These regions of interests will provide the local information for the neural network to predict which neighboring segments belong to the same neuron.

@@

Figure~\ref{fig:architecture} provides an overview of our architecture. 
Our network architecture has three layers of double convolutions followed by a max pooling step following the work of Chatfield et al. that found such a framework improves on single convolution layers~\cite{chatfield2014return}. The first two max pooling layers are anisotropic with pooling only in the $x$ and $y$ dimensions to account for the anisotropic nature of the datasets.
The output after this final pooling step is flattened into a 1-D vector which is input into two fully connected layers.
The final layer produces a probability with a sigmoid activation function~\cite{funahashi1989approximate}. 
All of the other activation functions are LeakyReLU~\cite{maas2013rectifier}. 
We use a stochastic gradient descent optimizer with Nesterov's accelerated gradient~\cite{nesterov1983method}. 
There are dropouts of $0.2$ after every pooling layer and the first dense layer, and a dropout of $0.5$ after the final dense layer. 
This prevents overfitting of the training data.

@@

\subsection{Agglomeration}

After constructing the graph structure we apply a graph-based segmentation strategy. 
There are many formulations of graph-based optimization strategies that provide different guarantees on their output. 
Neurons in the brain should be acyclic, i.e. the output shape should have a genus of zero. 
Current connectomics agglomeration techniques do not leverage this additional information but rather consider neighboring regions in successive order without regard to loop creation. 
In our graph formulation we enforce this topological property by applying a multicut partition onto the graph that generates a \textit{forest} on the nodes. 
A forest is a partitioning of a graph into a set of trees (i.e. no segment has a cycle). 
There are several heuristics that solve the multicut problem. For our purposes we use the greedy-additive algorithm~\cite{keuper2015efficient}.

>>>>

\subsection{Graph Creation}
\label{sec:skeletonization}
We generate nodes $N$ and edges $E$ to apply a graph-based optimization strategy for segmentation. 
In addition, these edges receive non-negative weights.

@@

The simplest node generation strategy creates one node for every unique segment label in the input volume.
However, some of the millions of labels in the volume correspond to very small volumes. 
Usually these locations have noisy image data so the pixel-based methods could not provide enough information to generate a larger segment.
It is difficult to extract useful shape features from these segments because of their small, and often random, shape. 
We prune these nodes from the graph by removing all segments with fewer than $20,000$ voxels. 
This removes XX\% of segments on a typical connectomics dataset.

@@

A na\"ive approach to generating edges produces an edge between all adjacent segments.
Two segments $l_1$ and $l_2$ are considered adjacent if there is a pair of adjacent voxels where one has label $l_1$ and the other has label $l_2$. 
NeuroProof and GALA consider all pairs of adjacent segments for merging. 
For us, this method produces too many edges in the graph. 
Therefore we present the following algorithm to identify pairs of segments to consider for merging.

First, we extract a skeleton from each segment using the TEASER algorithm~\cite{sato2000teasar,zhao2014automatic}.
Figure~\ref{fig:skeletonization} shows the skeletons in white of two segments from the label volume.
These skeletons consist of a sequence of \textit{joints}, locations that are a local maximum distance from the segment boundary, with line segments connecting successive joints. 
We prune the joints that are within $50$ voxels of each other to reduce unnecessary branching.
For the purposes of our algorithm, joints that have only one connected neighbor are referred to as \textit{endpoints}. 
Many of the segments that are erroneously split follow a similar pattern (Figure~\ref{fig:merge_candidates}). 
In these split instances the two skeletons have nearby endpoints.

After skeletonization, we begin to identify segments for merge consideration with the following two-pass heuristic.
In the first pass, we iterate over all endpoints $e$ belonging to a segment $S$ and create a set of segments $\mathbb{S}_e^\prime$ that includes all labels that have a single voxel within $t_{low}$ voxels from $e$. 
Elements of these sets are candidates for merging.
However the first pass often has too many candidates that should remain split so we apply an additional pass for further pruning.
In the second pass, we consider all of the segments $\mathbb{S}_e^\prime$ for every endpoint $e$. 
If a segment $S^\prime \in \mathbb{S}_e^\prime$ has an endpoint within $t_{high}$ voxels of $e$, the segment $S$ and $S^\prime$ are considered for merging. 
We store the midpoint between the two endpoints as the ``center" of the potential merge.

\begin{figure}[t]
	\centering
	\includegraphics[width=0.92\linewidth]{./figures/split_error1.png}
	\includegraphics[width=0.92\linewidth]{./figures/split_error2.png}
	\caption{Two erroneously split segments.}
	\label{fig:merge_candidates}
\end{figure}

@@

Our graph generation algorithm produces 3-D locations that require further consideration for merging. 
To determine which of these segments should actually merge, we train a 3-D CNN using the oversegmentation and the corresponding manually labeled ground truth data (Section~\ref{sec:dataset}).
We extract a cubic region of interest around these locations as input to the CNN. 
These regions of interest provide the local information for the neural network to predict which neighboring segments belong to the same neuron.

@@

Figure~\ref{fig:architecture} provides an overview of our architecture. 
Our network architecture has three layers of double convolutions followed by a max pooling step following the work of Chatfield et al. that found this technique improves on single convolution layers~\cite{chatfield2014return}. The first max pooling layer is anisotropic with pooling only in the $x$ and $y$ dimensions.
The output after this final pooling step is flattened into a 1-D vector which is input into two fully connected layers.
The final layer produces a probability with a sigmoid activation function~\cite{funahashi1989approximate}. 
All of the other activation functions are LeakyReLU~\cite{maas2013rectifier}. 
We use a stochastic gradient descent optimizer with Nesterov's accelerated gradient~\cite{nesterov1983method}. 
There are dropouts of $0.2$ after every pooling layer and the first dense layer, and a dropout of $0.5$ after the final dense layer to prevent overfitting. 
We discuss all other network parameters in Section~\ref{sec:network-parameters}.

@@

\subsection{Graph Partitioning}

After constructing the graph structure we apply a graph-based segmentation strategy. 
There are many graph partitioning minimization functions that provide different constraints on their output. 
Neurons in the brain should be acyclic (i.e. the output shape should have a genus of zero). 
We enforce this constraint by finding a multicut partition of the graph that generates a \textit{forest} on the nodes. 
A forest is a partitioning of a graph into a set of trees (i.e. no segment has a cycle). 
There are several heuristics that solve the multicut problem (which is NP-Hard). 
We use the greedy-additive algorithm~\cite{keuper2015efficient}.

### 2017-11-10 papers/cvpr2018/3_evaluation.tex
paper: updated entire paper

\paragraph{FlyEM.}
The FlyEM dataset comes from the mushroom body of a 5-day old adult male \textit{Drosophila} fly imaged by a focused ion-beam milling scanning electron microscopy.  
The mushroom body is this species is the major site of associative learning \cite{takemura2017connectome}. 
The original dataset contains a $\SI[product-units=single]{40 x 50 x 120}{\micro\meter}^3$ volume of which we use two cubes of size $\SI[product-units=single]{10 x 10 x 10}{\micro\meter}^3$. 
The resolution of this dataset is $\SI[product-units=single]{10 x 10 x 10}{\nano\meter}^3$ so each volume has $1000$ voxels in each dimension.

\paragraph{Segmentation Pipeline and Baseline.}
\label{sec:neuroproof}
The segmentation on the Kasthuri dataset was computed by agglomerating 3D supervoxels produced by zwatershed from 3D affinity predictions~\cite{zlateski2015image}. 
A recent study by Funke et.al. demonstrated superior performance of such method over existing ones on anisotropic data \cite{schlegel2017learning}. 
We learned 3d affinities in x,y,z using MALIS loss with a U-net~\cite{Turaga:2009,ronneberger2015u}. 
We apply the zwatershed algorithm, with suitable parameters, to compute an 3D over-segmentation of the volume. 
The resulting 3D over-segmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}. 
The VI values at different stopping thresholds of agglomeration correspond to the points on the curve plotted in Figure YYY.

We have collected two $1000 \times 1000 \times 1000$ voxel ($\SI[product-units=single]{10x10x10}{\micro\meter}^3$) volumes from the authors~\cite{takemura2017connectome}. 
Based on the authors' suggestion, we applied the context-aware delayed agglomeration algorithm~\cite{10.1371/journal.pone.0125825} that shows improved performance on this dataset than the pipeline used in the original publication. 
This segmentation framework learns voxel and supervoxel classifiers with an emphasis to minimize under-segmentation error.
At the same time this framework produces lower over-segmentation than standard algorithms. 
This algorithm first computes multi-channel 3D predictions for membranes, cell interiors, and mitochondria, among other cell features. 
The membrane prediction channel is utilized to produce an over-segmented volume using 3D watershed, which is then agglomerated hierarchically up to a certain confidence threshold. 
We used exactly same parameters for the publicly available code for this algorithm and used different agglomerations thresholds to plot the VI error curve.

@@

We prune potential merge candidates by running Algorithm \ref{alg:skeletonization} on the input dataset. 
There are two essential parameters to the algorithm: $t_{low}$ and $t_{high}$. 
Ideally, the merge candidates output by this algorithm will contains all possible positive examples with a very limited number of negative examples. 
After considering various thresholds, we find that $t_{low} = \SI{240}{\nano\meter}$ and $t_{high} = \SI{600}{\nano\meter}$ produces the best results given this objective function. 
Note that these thresholds are in nanometers and not voxels. 
Connectomics datasets often have different sample resolutions and downsampling in $z$. 
Using nanometers allows us to have uniform units across all of these datasets and calculate the thresholds in voxels at runtime. 
The thresholds are $t_{low} = (40, 40, 8)$ voxels and $t_{high} = (100, 100, 20)$ voxels for the Kasthuri dataset $t_{low} = (24, 24, 24)$ voxels and $t_{high} = (60, 60, 60)$ voxels for the FlyEM dataset.
The thresholds are anisotropic or isotropic depending on the corresponding isotropy of the dataset.
Table \ref{table:skeletonization} shows the overall success of this method of candidate pruning.

\subsection{Classifier Training}

We use the Kasthuri Vol. 1 dataset for training and validation. 
We train on 80\% of the potential merge candidates for this volume.
The validation the neural network classifier on the remaining 20\% of candidates. 
We consider networks with varying input sizes, optimizers, loss functions, filter sizes, learning rates, and activation functions. 
The supplemental material includes information on the experiments that determined these final parameters. 
Table \ref{table:architecture} provides the parameters in the final network.
There are 7,294,705 learnable parameters in our final architecture.
All the parameters are randomly initialized following the Xavier uniform distribution~\cite{glorot2010understanding}. 
Training concluded after 34 epochs.

@@

\subsection{Variation of Information}

We evaluate the performance of our methods using the split version of the variance of information~\cite{meila2003comparing}. 
Consider a ground truth labeling $GT$ and our automatically reconstructed segmentation $SG$. 
Over and undersegmentation are quanitified by the conditional entropy $H(GT | SG)$ and $H(SG | GT)$ respectively. 
Since we are measuring the entropy between two clusterings, better split variation of information scores are closer to the origin.

>>>>

\paragraph{FlyEM.}
The FlyEM dataset comes from the mushroom body of a 5-day old adult male \textit{Drosophila} fly imaged by a focused ion-beam milling scanning electron microscopy.  
The mushroom body in this species is the major site of associative learning \cite{takemura2017connectome}. 
The original dataset contains a $\SI[product-units=single]{40 x 50 x 120}{\micro\meter}^3$ volume of which we use two cubes of size $\SI[product-units=single]{10 x 10 x 10}{\micro\meter}^3$. 
The resolution of this dataset is $\SI[product-units=single]{10 x 10 x 10}{\nano\meter}^3$ so each volume has $1000$ voxels in each dimension.

\paragraph{Segmentation Pipeline and Baseline.}
\label{sec:neuroproof}
The segmentation on the Kasthuri dataset was computed by agglomerating 3-D supervoxels produced by zwatershed from 3-D affinity predictions~\cite{zlateski2015image}. 
A recent study by Funke et.al. demonstrated superior performance of such methods over existing ones on anisotropic data \cite{schlegel2017learning}. 
We learned 3-D affinities using MALIS loss with a U-net~\cite{Turaga:2009,ronneberger2015u}. 
We apply the zwatershed algorithm, with suitable parameters, to compute a 3-D oversegmentation of the volume. 
The resulting 3-D oversegmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}. 
The variation of information (Section~\ref{sec:variation-of-information}) values at different stopping thresholds of agglomeration correspond to the curve plotted in Figure~\ref{fig:variation-of-information}.

We have collected two $1000 \times 1000 \times 1000$ voxel ($\SI[product-units=single]{10x10x10}{\micro\meter}^3$) volumes from the authors~\cite{takemura2017connectome}. 
Based on the authors' suggestion, we applied the context-aware delayed agglomeration algorithm~\cite{10.1371/journal.pone.0125825} that shows improved performance on this dataset over the pipeline used in the original publication. 
This segmentation framework learns voxel and supervoxel classifiers with an emphasis to minimize undersegmentation error.
At the same time this framework produces lower over-segmentation than standard algorithms. 
This algorithm first computes multi-channel 3-D predictions for membranes, cell interiors, and mitochondria, among other cell features. 
The membrane prediction channel is utilized to produce an oversegmented volume using 3-D watershed, which is then agglomerated hierarchically up to a certain confidence threshold. 
We used exactly the same parameters for the publicly available code for this algorithm and used different agglomerations thresholds to plot the variation of information error curve.

@@

We prune potential merge candidates with the algorithm described in Section~\ref{sec:skeletonization}. 
There are two essential parameters to the algorithm: $t_{low}$ and $t_{high}$. 
Ideally, the merge candidates output by this algorithm will contains all possible positive examples with a very limited number of negative examples. 
After considering various thresholds, we find that $t_{low} = \SI{240}{\nano\meter}$ and $t_{high} = \SI{600}{\nano\meter}$ produces the best results given this objective function. 
Note that these thresholds are in nanometers and not voxels. 
Connectomics datasets often have different sample resolutions and downsampling in $z$. 
Using nanometers allows us to have uniform units across all of these datasets and calculate the thresholds in voxels at runtime. 
The thresholds are $t_{low} = (40, 40, 8)$ voxels and $t_{high} = (100, 100, 20)$ voxels for the Kasthuri dataset and $t_{low} = (24, 24, 24)$ voxels and $t_{high} = (60, 60, 60)$ voxels for the FlyEM dataset.
The thresholds are anisotropic or isotropic depending on the corresponding isotropy of the dataset.
Table \ref{table:skeletonization} shows the overall success of this method of candidate pruning.

\subsection{Classifier Training}
\label{sec:network-parameters}
We use the Kasthuri Vol. 1 dataset for training and validation. 
We train on 80\% of the potential merge candidates for this volume.
We validate the neural network classifier on the remaining 20\% of candidates. 
We consider networks with varying input sizes, optimizers, loss functions, filter sizes, learning rates, and activation functions. 
The supplemental material includes information on the experiments that determined these final parameters. 
Table \ref{table:architecture} provides the parameters in the final network.
There are 7,294,705 learnable parameters in our final architecture.
All the parameters are randomly initialized following the Xavier uniform distribution~\cite{glorot2010understanding}. 
Training concluded after 34 epochs.

@@

\subsection{Variation of Information}
\label{sec:variation-of-information}
We evaluate the performance of our methods using the split version of variance of information~\cite{meila2003comparing}. 
Consider a ground truth labeling $GT$ and our automatically reconstructed segmentation $SG$. 
Over and undersegmentation are quanitified by the conditional entropy $H(GT | SG)$ and $H(SG | GT)$ respectively. 
Since we are measuring the entropy between two clusterings, better split variation of information scores are closer to the origin.

### 2017-11-10 papers/cvpr2018/4_results.tex
paper: updated entire paper

Table \ref{table:skeletonization} shows the results of pruning using the skeletonization heuristic.
The baseline algorithm considers all adjacent regions for merging. 
Our method removes a significant portion of these candidates while maintaining a large number of the true merge locations.
This edge pruning is essential for the graph partitioning algorithms which have a computational complexity dependence on the number of edges. 
Our pruning heuristic removes at least $6\times$ the number of edges between correctly split segments on all datasets, achieving a maximum removal ratio of $20\times$. 
Equally important is the number of split errors that remain after pruning.
These are the locations that we want to merge to create a more accurate reconstruction.
For every dataset, the number of positive candidates remains relatively even. 
However, since our heuristic does not enforce an adjacency constraint of two regions when constructing edges in the graph, the difference does not indicate the number of examples excluded by pruning. 
In fact, our method finds a number of examples which are non-adjacent.
Figure \ref{fig:skeleton-results} shows two example segments which are split errors.
The top example our algorithm missed but the segments are adjacent. 
The bottom example our algorithm found despite the fact that they are not adjacent.

@@

Table \ref{table:classification} shows the precision and recall for all of the datasets. 
Our methods are more general than traditional connectomics examples allowing us to train the network on an anisotropic dataset and get impressive results on an isotropic dataset. 
Our initial network does not take in any image data, only the segment shapes, so we merely extract the $1200 \textrm{nm}^3$ region from any dataset and rescale as input into the neural network. 
Figure \ref{fig:network-results} shows the receiver operating characteristic (ROC) curve for all four datasets.

\begin{figure}
	\includegraphics[width=0.9\linewidth]{./figures/roc-microns-300-test.png}
	\caption{The receiver operating characteristic (ROC) curve for all four datasets.}
	\label{fig:network-results}
\end{figure}

@@

@@

The final metric for comparing two connectomics segmentations is computing the variation of information with respect to an expert-labeled ground truth dataset. Figure \ref{fig:variation-of-information} shows the results on the datasets compared to the baseline (green) and an oracle (blue).

>>>>

Table \ref{table:skeletonization} shows the results of pruning using the skeletonization heuristic.
The baseline algorithm considers all adjacent regions for merging. 
Our method removes a significant portion of these candidates while maintaining a large number of the true merge locations.
This edge pruning is essential for the graph partitioning algorithm which has a computational complexity dependence on the number of edges. 
Our pruning heuristic removes at least $6\times$ the number of edges between correctly split segments on all datasets, achieving a maximum removal ratio of $20\times$. 
Equally important is the number of split errors that remain after pruning.
These are the locations that we want to merge to create a more accurate reconstruction.
For every dataset, the number of positive candidates remains relatively even. 
However, since our heuristic does not enforce an adjacency constraint of two regions when constructing edges in the graph, the difference does not indicate the number of examples excluded by pruning. 
In fact, our method finds a number of examples which are non-adjacent.
Figure \ref{fig:skeleton-results} shows two example segments which are split errors.
The top example our algorithm missed but the segments are adjacent. 
The bottom example our algorithm found despite the fact that they are not adjacent.

@@

Table \ref{table:classification} shows the precision and recall for all of the datasets. 
Since, our method does not rely on the image data, we can train the network on an anisotropic dataset and get impressive results on an isotropic dataset. 
Figure \ref{fig:network-results} shows the receiver operating characteristic (ROC) curve for all four datasets.

\begin{figure}
	\includegraphics[width=0.9\linewidth]{./figures/roc-microns-300-test.png}
	\caption{(NOT CORRECT) The receiver operating characteristic (ROC) curve for all four datasets.}
	\label{fig:network-results}
\end{figure}

TODO - ADD QUALITATIVE RESULTS

@@

TODO - QUANTIFY IMPROVEMENT BY MULTICUT - READERS CAN SKIP SECTION FOR NOW

@@

We compute the variation of information for our segmentations against the expert-labeled ground truth datasets. 
The input segmentation to our network serves as a baseline. 
We evaluate NeuroProof (our input) at several different thresholds to create a variation of information curve. 
Similarly, we run the greedy-additive heuristic with varying parameters that increase the probability needed for merging nodes. 
Figure \ref{fig:variation-of-information} shows the results on the datasets compared to the baseline (green) and an oracle (blue). 
The oracles sees the entire constructed graph from our algorithm and correctly partitions the graph based on the ground truth. 
Our methods decreases the split variation of information by a factor of XX\% and only increases the merge variation of information by a factor of XX\% on the test datasets. 
Table \ref{table:variation-of-information} provides a quantitative overview for the changes in variation of information.

TODO - ADD QUALITATIVE RESULTS

\begin{table}
	\centering
	\begin{tabular}{c c c} \hline
		\textbf{Dataset} & \textbf{VI Split} & \textbf{VI Merge} \\ \hline
		Kasthuri Training &  & \\
		Kasthuri Testing & & \\
		FlyEM Vol. 1 & & \\
		FlyEM Vol. 2 & & \\ \hline
	\end{tabular}
	\caption{Variation of Information Change}
	\label{table:variation-of-information}
\end{table}

### 2017-11-10 papers/cvpr2018/5_conclusions.tex
paper: updated entire paper

We present a novel method for framework neuronal processes in connectomics image datasets.
We extend on top of existing region-based agglomeration strategies and show significant accuracy improvement on two datasets from two different species. 
By extracting skeletons from every segment in the input we can quickly produce a graph with $N$ nodes and $E$ weighted edges from the input. 
We populate the edge weights using a 3-D CNN that, unlike previous methods, does not use the raw image data.
Separating the neural network from the images allows us to train on anisotropic data and test on isotropic data with different sample resolution. 
This is exceptionally important in connectomics because of the extreme labor-intensive cost of manually segmenting ground truth data.

>>>>

We present a novel method for framework neuronal processes in connectomics image datasets.
We extend on top of existing region-based agglomeration strategies and show significant accuracy improvement on two datasets from two different species. 
By extracting skeletons from every segment in the input we can quickly produce a graph $G$ with $N$ nodes and $E$ weighted edges from the input. 
We populate the edge weights using a 3-D CNN that, unlike previous methods, does not use the raw image data.
Separating the neural network from the images allows us to train on anisotropic data and test on isotropic data with different sample resolution. 
This is exceptionally important in connectomics because of the extreme labor-intensive cost of manually segmenting ground truth data. 
We use existing graph partitioning strategies on the $G$, enabling us to enforce domain-constraints on the resulting segmentation.
For us, our constraints follow from the topology of neurons.
However, this framework extends to other domains with varying constraints.
